%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Habibullah ``Habib'' Pagarkar} % Your name
\address{
  \href{mailto:habibpagarkar@gmail.com}{habibpagarkar@gmail.com}
  \\ \href{http://github.com/habib}{github.com/habib}} % Your email and web-site address
\address{10422 Huebner Road, Apt 2610 \\ San Antonio, TX 78240 \\ (312) 402-8041} % Your address

\begin{document}
\vspace{1em}

%----------------------------------------------------------------------------------------
%       PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Summary}
Technical management professional possessing extensive experience working
with distributed multi-disciplinary teams. I have significant
understanding of agile project management and continual improvement principles. Recognized for
empowering and transforming small teams to rapidly deliver high quality software.
\end{rSection}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE WITH THOUGHTWORKS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience with ThoughtWorks}

\begin{rSubsection}{Client: Rackspace}{San Antonio, TX}{Jun
    12}{present}
{Program Manager on a multi-year engagement to help Rackspace run
  First Generation Cloud Servers and build the OpenStack based Next
  Generation Cloud Servers.}

\item Co-ordinate activities across 6 teams
  totaling 35 consultants located in 4 continents
\item Work with product team to prioritize features and allocate dev capacity
\item Liase the consulting teams with numerous corporate groups to address task blockers
\item Trouble-shoot issues in production, follow
  through on resolution and plan for long-term improvements
\item Responsible for staffing and consultant's career growth
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Client: A leading management consulting
    firm}{Gurgaon, India}{Apr 11}{May 12}
{Adopted a Software Architect/Project Manager hybrid role and led 10 consultants to re-write the
  client's partner compensation calculation system. Showcased delivery
  capability which established ThoughtWorks' reputation as the go-to company for developing complicated custom software.}

\item Rescued a failing re-write attempt of a legacy Oracle Financials
  application
\item Introduced results-based agile software delivery
  methodology to the client's accountants. This included quick
  adjustments of features based on changing business requirements, innovative
  project health-checks, frequent demos and creating an extensive set
  of acceptance tests
\item Mentored consultants put into stretch roles to ensure their
  success
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Client: GSM Association}{Bangalore, India}{Dec 10}{Mar 11}{Tech-lead on a team of 10 consultants working with a non-profit
  and its 5 partners. Wrote the application using Ruby on Rails to
  rapidly incorporate feedback to meet challenging deadlines.}
\item Created a charity to let users donate their cell phone plan's text messaging
  balance to non-profits
\item Application was released publicly at the GSM Mobile World Congress held at Barcelona in Feb 2011
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Client: Rackspace}{Bangalore, India \& San Antonio,
  TX}{Jan 09}{Dec
    10}
{Tech Lead on a skunkworks-style distributed dev team comprising of 8
  ThoughtWorkers and 8 Rackers. Developed applications that are the
  lynchpins of Rackspace's Dedicated and Cloud hosting businesses.}

\item Team pioneered Continuous Delivery techniques within the organization
\item Built mission critical data center management system used by
  data center ops \& network admins to:
\vspace{-0.5em}
\begin{itemize}  \itemsep0.5pt \parskip0pt
    \item[$\ast$] Configure networking gear like switches, firewalls and load-balancers
    \item[$\ast$] Manage company-wide DNS
    \item[$\ast$] Identify free cabinet space and monitor data center power consumption
    \item[$\ast$] Automate discovery of devices and servers, allocate IP addresses and kick-start servers
\end{itemize}
\item These, and other tools, reduced the time taken to provision a server from 8 days to 18 minutes
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PREVIOUS WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Previous Work Experience}

\begin{rSubsection}{Teleonto}{Hyderabad, India}{}{}
{Senior Software Engineer}
\item Worked on the onsite SaaS offerings of Revenue Assurance and Revenue Intelligence Analytics for Telecom firms as part of the 9 member Analytics team
\item Contributed to the revenue leakage and churn analysis modules written in Common Lisp
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Sahakriya}{Mumbai, India}{}{}{Independent Software Consultant}
\item Performed entire SDLC of {\em SecureSignIn}, a patent pending solution for two-factor authentication, that provides a secure e-banking environment
\item Built a Java SE PC application and Java ME mobile application on demand with a unique one-time use PIN using a cryptographically strong algorithm
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{2Wire}{San Jose, CA}{}{}{Software Engineer}
\item Worked in a 4 member team to create {\em MediaScout}, a client
  application that manages multimedia present on the {\em MediaPortal}
  (a next-gen set top box and digital media server) and the user's computer
\item Ported the C++ application from Windows to Mac OS X and created a cross-platform installer
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	COMMUNITY INVOLVEMENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Community Involvement}

Core member of the organizing team behind RubyConf India 2011, India's
premier Ruby conference. Also helped organize RubyConf India 2010 and
2012. Speaker at multiple external and internal conferences. Occasional
contributor to a few Emacs modes.
\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Tools Used}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Ruby, Python, JavaScript, Common Lisp, Clojure, Java, C++ \\
Databases & MySQL, PostgreSQL, Oracle 11i \\
Build and Deploy & CC.rb, Jenkins, TeamCity \\
Other Tools & Git, SVN, Perforce, Emacs, RedMine \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Johns Hopkins University} \hfill Baltimore, MD. Aug 03 {\em to} Jun 05 \\ 
M.S.E. in Computer Science \& Engineering


{\bf Mumbai University, V.E.S. Institute of Technology} \hfill Mumbai, India. Aug 99 {\em to} Jun 03 \\ 
B.E. in Information Technology

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
